Using pressure-driven flow systems to evaluate laser speckle contrast imaging

### 2022-09-12 article.tex
Add grant numbers and update Andy's bio
Update disclosures

% ----------------------------------------------------------------------------------------
% BEGIN DISCLOSURES AND ACKNOWLEDGEMENTS
% ----------------------------------------------------------------------------------------
\subsection*{Disclosures}
A.K.D. holds equity in and serves on the board of directors of Dynamic Light, Inc. The authors declare no other conflicts of interest.

@@

\subsection*{Acknowledgments}
This study was supported by the National Institutes of Health (Nos. ?)

@@

\vspace{2ex}\noindent\textbf{Andrew K. Dunn} is the Edward S. Hyman Endowed Chair in Engineering in the Department of Biomedical Engineering and the Director of the Center for Emerging Imaging Technologies (CEIT) at the University of Texas at Austin. He pioneered the use of laser speckle contrast imaging to measure blood flow in the brain and has more than 50 publications on the subject. His research focuses on the development of novel optical imaging techniques for studying the brain.

>>>>

% ----------------------------------------------------------------------------------------
% BEGIN DISCLOSURES AND ACKNOWLEDGEMENTS
% ----------------------------------------------------------------------------------------
\subsection*{Disclosures}
The authors declare no conflicts of interest.

@@

\subsection*{Acknowledgments}
This study was supported by the National Institutes of Health (Nos. NS108484 and EB011556) and the UT Austin Portugal Program.

@@

\vspace{2ex}\noindent\textbf{Andrew K. Dunn} is the Edward S. Hyman Endowed Chair in Engineering in the Department of Biomedical Engineering and the Director of the Center for Emerging Imaging Technologies (CEIT) at the University of Texas at Austin. He pioneered the use of laser speckle contrast imaging to measure blood flow in the brain. His research focuses on the development of novel optical imaging techniques for studying the brain.
